### 2024-08-30 download-football-data.qmd
20240830 - additional NFL data

A Data Dictionary for rosters is located at the following link: <https://nflreadr.nflverse.com/articles/dictionary_rosters.html>

@@

nfl_rosters_weekly_raw <- progressr::with_progress(
  nflreadr::load_rosters_weekly(seasons = TRUE))
```

@@

save(
  nfl_rosters_raw,
  file = "./data/nfl_rosters_raw.RData"
)

@@

```{r}
nfl_rosters <- nfl_rosters_raw %>% 
  select(gsis_id, season, team, week, everything()) %>% 
  arrange(full_name, gsis_id, season, team, week)
```

@@

@@

@@

>>>>

A Data Dictionary for rosters is located at the following links:

- <https://nflreadr.nflverse.com/articles/dictionary_rosters.html>
- <https://github.com/nflverse/nfldata/blob/master/DATASETS.md#rosters>

@@

nfl_rosters_weekly_raw <- progressr::with_progress(
  nflreadr::load_rosters_weekly(seasons = TRUE))

rosters <- read_csv("https://raw.githubusercontent.com/leesharpe/nfldata/master/data/rosters.csv")
```

@@

save(
  nfl_rosters_raw,
  rosters,
  file = "./data/nfl_rosters_raw.RData"
)

@@

```{r}
nfl_rosters <- nfl_rosters_raw %>% 
  left_join(
    rosters %>% select(playerid, season, team, side, category, games, starts, years, av),
    by = c("season","team","pfr_id" = "playerid"),
    na_matches = "never"
  ) %>% 
  select(gsis_id, season, team, week, everything()) %>% 
  arrange(full_name, gsis_id, season, team, week)
```

@@

### Standings {#sec-standings}

A Data Dictionary for game schedules data is located at the following link: <https://github.com/nflverse/nfldata/blob/master/DATASETS.md#standings>

nfl_standings_raw <- read_csv("http://www.habitatring.com/standings.csv")
```

save(
  nfl_standings_raw,
  file = "./data/nfl_standings_raw.RData"
)
```

load(file = "./data/nfl_standings_raw.RData")
```

The `nfl_standings` object is in `season`-`team` form.
That is, each row should be uniquely identified by the combination of `season` and `team`.

```{r}
nfl_standings <- nfl_standings_raw
```

Let's check for duplicate `season`-`team` instances:

```{r}
nfl_standings %>% 
  group_by(season, team) %>% 
  filter(n() > 1) %>% 
  head()
```

save(
  nfl_standings,
  file = "./data/nfl_standings.RData"
)
```

load(file = "./data/nfl_standings.RData")
```

@@

### Draft Values {#sec-draftValues}

A Data Dictionary for draft values data is located at the following link: <https://github.com/nflverse/nfldata/blob/master/DATASETS.md#draft_values>

nfl_draftValues_raw <- read_csv("https://raw.githubusercontent.com/leesharpe/nfldata/master/data/draft_values.csv")
```

save(
  nfl_draftValues_raw,
  file = "./data/nfl_draftValues_raw.RData"
)
```

load(file = "./data/nfl_draftValues_raw.RData")
```

The `nfl_draftValues` object is in `pick` form.
That is, each row should be uniquely identified by `pick`.
Let's rearrange the data accordingly:

```{r}
nfl_draftValues <- nfl_draftValues_raw %>% 
  select(pick, everything()) %>% 
  arrange(pick)
```

Let's check for duplicate `pick` instances:

```{r}
nfl_draftValues %>% 
  group_by(pick) %>% 
  filter(n() > 1) %>% 
  head()
```

save(
  nfl_draftValues,
  file = "./data/nfl_draftValues.RData"
)
```

load(file = "./data/nfl_draftValues.RData")
```

@@

### Trades {#sec-trades}

A Data Dictionary for game schedules data is located at the following link: <https://github.com/nflverse/nfldata/blob/master/DATASETS.md#trades>

nfl_trades_raw <- read_csv("https://raw.githubusercontent.com/leesharpe/nfldata/master/data/trades.csv")
```

save(
  nfl_trades_raw,
  file = "./data/nfl_trades_raw.RData"
)
```

load(file = "./data/nfl_trades_raw.RData")
```

The `nfl_trades` object is in `trade`-`player` form.
That is, each row should be uniquely identified by the combination of `trade_id` and `pfr_id`.

```{r}
nfl_trades <- nfl_trades_raw
```

Let's check for duplicate `trade`-`player` instances:

```{r}
nfl_trades %>%
  filter(!is.na(pfr_id)) %>% 
  group_by(trade_id, pfr_id) %>% 
  filter(n() > 1) %>% 
  head()
```

save(
  nfl_trades,
  file = "./data/nfl_trades.RData"
)
```

load(file = "./data/nfl_trades.RData")
```
